---
title: "capstone2ndTask_ver3"
author: "Monica, Vanessa, Veronica"
date: "17 June 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Load libraries
```{r library}
library(VIM)
library(mice)
library(rms)
library(graphics)
library(dplyr)
library(MASS)
library(stats)
library(base)
```
#Load dataset
```{r data}
setwd("C:/Users/Asus/OneDrive - Universitas Pelita Harapan/capstone/tugas #2/R FILES")
df_train = read.csv("dengue_features_train.csv")
dl_train = read.csv("dengue_labels_train.csv")
df_test = read.csv("dengue_features_test.csv")
dl_test = read.csv("submission_format.csv")
```
#Summary of data
```{r summary}
str(df_train)
summary(df_train)
sum(!complete.cases(df_train)) 
(y = sum(is.na(df_train)))

str(dl_train)
summary(dl_train)

str(df_test)
summary(df_test)

```

#filter train data by city, San Jose and Iquitos
```{r city}
dl_train_sj <- filter(dl_train, city == 'sj')
summary(dl_train_sj)
df_train_sj <- filter(df_train, city == 'sj')

dl_train_iq <- filter(dl_train, city == 'iq')
summary(dl_train_iq)
df_train_iq <- filter(df_train, city == 'iq')
```
#remove categorical variables to prepare data for imputation
```{r remove}
df_train_sj_num <- subset(df_train_sj, select = -c(city, week_start_date))
df_train_iq_num <- subset(df_train_iq, select = -c(city, week_start_date))
```
#imputation for train data
```{r impute}
impute_dft_sj <- mice(df_train_sj_num, m=1, seed = 123, print = FALSE)
impute_dft_iq <- mice(df_train_iq_num, m=1, seed = 123, print = FALSE)

#store completed data (with no NAs)
imp_df_train_sj <-complete(impute_dft_sj,1)
imp_df_train_iq <- complete(impute_dft_iq,1)
colnames(imp_df_train_sj)[colSums(is.na(imp_df_train_sj)) > 0]
colnames(imp_df_train_iq)[colSums(is.na(imp_df_train_iq)) > 0]

```
#imputation for test data
``` {r impute test data}
df_test_mice <- mice(df_test, m=1, seed = 123, print = FALSE)
complete_df_test <-complete(df_test_mice,1)
complete_df_test['total_cases'] <- NA
df_test_sj <- filter(complete_df_test, city == 'sj')
df_test_iq <- filter(complete_df_test, city == 'iq')
df_test_sj <- subset(df_test_sj, select = -c(city, week_start_date))
df_test_iq <- subset(df_test_iq, select = -c(city, week_start_date))
```
#see correlation between station_precip_mm, precipitation_amt_mm, reanalysis_sat_precip_amt_mm, reanalysis_precip_amt_kg_per_m2 because it all holds the same title: Total Precipitation
```{r correlation percipitation}
library(psych)
percipitation_sj <- subset(imp_df_train_sj, select = c(station_precip_mm, precipitation_amt_mm,
                                                 reanalysis_sat_precip_amt_mm, reanalysis_precip_amt_kg_per_m2))
pairs.panels(percipitation_sj,
             method = "spearman", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipse
)

percipitation_iq <- subset(imp_df_train_iq, select = c(station_precip_mm, precipitation_amt_mm,
                                                 reanalysis_sat_precip_amt_mm, reanalysis_precip_amt_kg_per_m2))
pairs.panels(percipitation_iq,
             method = "spearman", # correlation method
             hist.col = "#00AFBB",
             density = TRUE,  # show density plots
             ellipses = TRUE # show correlation ellipse
)


##correlation coef for precipitation_amt_mm and reanalysis_sat_precip_amt_mm = 1.00, delete reanalysis_sat_precip_amt
imp_df_train_iq <- subset(imp_df_train_iq, select = -c(reanalysis_sat_precip_amt_mm))
imp_df_train_iq

imp_df_train_sj <- subset(imp_df_train_sj, select = -c(reanalysis_sat_precip_amt_mm))
imp_df_train_sj
```

##remove year and weekofyear since it is a timescale and not a variable:
``` {r remove}
imp_df_train_iq <- subset(imp_df_train_iq, select = -c(year, weekofyear))
imp_df_train_iq

imp_df_train_sj <- subset(imp_df_train_sj, select = -c(year, weekofyear))
imp_df_train_sj
```
#see amount of rows with missing data
```{r check na in data}
(y_sj = sum(is.na(imp_df_train_sj)))
(y_iq = sum(is.na(imp_df_train_iq)))
```

#labels train data processing 
``` {r label processing}
imp_df_train_sj$total_cases <- dl_train_sj$total_cases

imp_df_train_iq$total_cases <- dl_train_iq$total_cases
```
#see correlation with total_cases
```{r correlation}
library(lares)
#SJ
corr_var(imp_df_train_sj, # name of dataset
         ignore = c("year", "weekofyear"),
         total_cases, # name of variable to focus on
         top = 10, # display top 5 correlations
         method = "spearman"
) 
#IQ
corr_var(imp_df_train_iq, # name of dataset
         ignore = c("year", "weekofyear"),
         total_cases, # name of variable to focus on
         top = 10, # display top 5 correlations
         method = "spearman"
) 
```
#build formula for 10 highest correlation between predictor variables and response variable
```{r formula_top10correlation}
formula_10corr_sj <- formula(total_cases ~ reanalysis_specific_humidity_g_per_kg + reanalysis_dew_point_temp_k
                             + reanalysis_min_air_temp_k + reanalysis_precip_amt_kg_per_m2 + reanalysis_air_temp_k
                             + reanalysis_max_air_temp_k + reanalysis_avg_temp_k + 
                               reanalysis_relative_humidity_percent + station_min_temp_c + station_avg_temp_c)

formula_10corr_iq <- formula(total_cases ~ reanalysis_specific_humidity_g_per_kg + reanalysis_dew_point_temp_k
                             + reanalysis_min_air_temp_k + station_min_temp_c + reanalysis_precip_amt_kg_per_m2
                             + reanalysis_relative_humidity_percent + station_avg_temp_c + reanalysis_tdtr_k 
                             +precipitation_amt_mm + reanalysis_air_temp_k)
```

#build model with GLM POISSON 
``` {r poismodtop10corr}
#SJ
mod_top10_sj <- glm(formula_10corr_sj, family="poisson", data=imp_df_train_sj, contrasts = NULL)
summary(mod_top10_sj)
#AIC = 39133
#dev/df = 37.26

#IQ
mod_top10_iq <- glm(formula_10corr_iq, family="poisson", data=imp_df_train_iq, contrasts = NULL)
summary(mod_top10_iq)
#AIC = 6305.4
#dev/df = 9.32
```

#see performance of model
```{r performance}
library(performance)
check_collinearity(mod_top10_sj)
check_collinearity(mod_top10_iq)
```
#remove highest VIF value
```{r formula_filteredByVIF}

formula_vif1_sj <- formula(total_cases ~  reanalysis_precip_amt_kg_per_m2+ station_min_temp_c + 
                             station_avg_temp_c)

formula_vif1_iq <- formula(total_cases ~  reanalysis_min_air_temp_k + station_min_temp_c + 
                             reanalysis_precip_amt_kg_per_m2
                             +station_avg_temp_c + reanalysis_tdtr_k 
                             +precipitation_amt_mm )
```
#build new glm-poisson model
```{r new poisson}
#SJ
mod_vif1p_sj <- glm(formula_vif1_sj,  family = "poisson",data=imp_df_train_sj, contrasts = NULL)
summary(mod_vif1p_sj)
#AIC = 40615
#dev/df = 38.7
#IQ
mod_vif1p_iq <- glm(formula_vif1_iq,  family = "poisson",data=imp_df_train_iq, contrasts = NULL)
summary(mod_vif1p_iq)
#AIC = 6414.7
#dev/df = 9.48
```

#build new glm-nb model and see AIC
``` {r modRemoveHighVIF}
#SJ
mod_vif1_sj <- glm.nb(formula_vif1_sj,  data=imp_df_train_sj, contrasts = NULL)
summary(mod_vif1_sj)
#AIC = 8412.2
#dev/df = 1.128



#IQ
mod_vif1_iq <- glm.nb(formula_vif1_iq, data=imp_df_train_iq, contrasts = NULL)
summary(mod_vif1_iq)
#AIC = 3149.3
#dev/df = 1.16
```
#predict on test data 
``` {r predict}
submission_sj_20 <-predict(mod_vif1_sj, df_test_sj, type="response", se.fit=TRUE)
test_20_sj<- submission_sj_20$fit

submission_iq_20 <-predict(mod_vif1_iq, df_test_iq, type="response", se.fit=TRUE)
test_20_iq<- submission_iq_20$fit
```
#prepare submission file
``` {r submission file}
#submission_format <- read.csv("submission_format.csv")
dl_test$total_cases <-
  as.numeric(c(test_20_sj, test_20_iq))

dl_test$total_cases <- 
  round(dl_test$total_cases, 0)

write.csv(dl_test,file = 'ModelTiani_trialNBVIF.csv', row.names = F)
```

#build new formula with p-value <0.05
```{r forPickSgnfPValue}

formula_pv_sj <- formula(total_cases ~  reanalysis_precip_amt_kg_per_m2+  station_avg_temp_c)

formula_pv_iq <- formula(total_cases ~  reanalysis_min_air_temp_k + station_min_temp_c)
```
#build new glm-nb model and see AIC
``` {r modPickSgnfPValue}
#SJ
mod_pv_sj <- glm.nb(formula_pv_sj,  data=imp_df_train_sj, contrasts = NULL)
summary(mod_pv_sj)
#AIC = 8412.7
#dev/df = 1.127

#IQ
mod_pv_iq <- glm.nb(formula_pv_iq, data=imp_df_train_iq, contrasts = NULL)
summary(mod_pv_iq)
#AIC = 3142.7
#dev/df = 1.15
```

#predict on test data 
``` {r predict}
submission_sj_19 <-predict(mod_pv_sj, df_test_sj, type="response", se.fit=TRUE)
test_19_sj<- submission_sj_19$fit

submission_iq_19 <-predict(mod_pv_iq, df_test_iq, type="response", se.fit=TRUE)
test_19_iq<- submission_iq_19$fit
```
#prepare submission file
``` {r submission file}
submission_format <- read.csv("submission_format.csv")
submission_format$total_cases <-
  as.numeric(c(test_19_sj, test_19_iq))

submission_format$total_cases <- 
  round(submission_format$total_cases, 0)

write.csv(submission_format,file = 'ModelTiani_trial1.csv', row.names = F)
```
